---
title: "Shiny App project"
author: "Lanark"
date: "`r Sys.Date()`"
output: html_document
---

This is the document intended to be used for the Shiny app task as
instructed by the Group project Assignment. 
Please be aware teammates working on the same lines of code to avoid conflicts. 
Please pull before starting to work on a section. 
Please save, commmit and push after finshing work. 

```{r}
library(shiny)
library(shinydashboard)
library(shinydashboardPlus)
library(shinyWidgets)
library(shinythemes)
library(tidyquant)
library(tidyverse)
library(ggplot2)
library(plotly)
library(DT)
library(dashboardthemes)
```


Task 1 Shiny app 
```{r}
stock_data <- function(ticker, date_beg, date_end) {
  data <- getSymbols(ticker, 
                   from = date_beg,
                   to = date_end,
                   warnings = FALSE,
                   auto.assign = FALSE,
                   src = 'yahoo', 
                   periodicity = "daily"
                   )
  
}

  # Load in Stock tickers
  NYSE <- read.delim("data/NYSE.txt", stringsAsFactors = FALSE)
  NASDAQ <- read.delim("data/NASDAQ.txt", stringsAsFactors = FALSE)
  LSE <- read.delim("data/LSE.txt", stringsAsFactors = FALSE)
  
  # Combine into one list
  tickers <- rbind(NASDAQ, NYSE, LSE)
  
  # Remove duplicants
  tickers <- distinct(tickers)
  
  # Create new nice column for choices
  tickers$options = paste0(tickers$Symbol, "-", tickers$Description)
me <- stock_data("AAPL", "2021-01-01", "2022-01-01")

#fake <- tq_get("AAPL", get = "key.stats", from = "2021-01-01", to = "2022-01-01")
#tq_get

#plot_ly(data = fake, x = fake$date , type = "candlestick", open = fake$open , close = fake$close, high = fake$high, low = fake$low)

shinyApp(ui,server)

```

Learn to loop through prices and generate a bunch of data sets and graphs
Maybe create tab that lets you make pie chart of market caps
Look into tables for app

Could make a daily move price charts, with real-time price changes
then have 15 minute refreshing data

Create a tab to compare selected stock returns
select 6 initial stocks to display
make data refresh every hour
add refresh button
create a tab that compares selected stock market caps, pie chart
Look into how to lay out plots
Could do losers and gainers, boxes of who up last month and who down

Maybe create a thing that lets you create optimal portfolio




